\subsection{Valuation}

Valuing cryptocurrencies presents unique challenges and opportunities compared to traditional assets. The decentralized and digital nature of these assets requires innovative approaches to determine their intrinsic and market values. Below, we discuss key valuation techniques as well as metrics related to the valuation models.

When valuing assets, we can explore both relative valuation models and absolute valuation models. Relative valuation models compare the value of a cryptocurrency to other similar assets, providing a framework to assess whether a cryptocurrency is overvalued or undervalued relative to its peers.


Relative valuation models compare the value of a cryptocurrency to other similar assets, providing a framework to assess whether a cryptocurrency is overvalued or undervalued relative to its peers. One of the most widely used relative valuation models in the cryptocurrency space is the Network Value to Transactions (NVT) ratio.

\subsubsection{P/E Ratio}

The Price-to-Earnings (P/E) ratio is a commonly used metric in equity markets to assess the valuation of a company's stock. It measures the ratio of the company's current market price per share to its earnings per share (EPS). The formula for calculating the P/E ratio is as follows:

\begin{equation}\label{eq:pe_ratio}
\text{P/E Ratio} = \frac{\text{Market Price per Share}}{\text{Earnings per Share}}
\end{equation}

- \textbf{Market Price per Share}: The current market price of the company's stock.
- \textbf{Earnings per Share (EPS)}: The company's net income divided by the total number of outstanding shares.

The P/E ratio provides insights into how much investors are willing to pay for each unit of earnings generated by the company. A high P/E ratio may indicate that investors expect high growth potential from the company, while a low P/E ratio may suggest undervaluation or slower growth prospects.


\subsubsection{NVT Ratio}

Similar to the price-to-earnings (P/E) ratio, the NVT ratio is calculated by dividing the market capitalization of a cryptocurrency by its daily transaction volume.

\begin{equation}\label{eq:nvt_ratio}
\text{NVT Ratio} = \frac{\text{Market Capitalization}}{\text{Daily Transaction Volume}}
\end{equation}


$ \bullet $ \textbf{Market Capitalization}: The total value of all coins in circulation, calculated by multiplying the current price by the total supply.

$ \bullet $  \textbf{Daily Transaction Volume}: The sum of all transactions made within a 24-hour period.

\subsection{Absolute Valuation Models}

Absolute valuation models provide an alternative approach to valuing cryptocurrencies. The Equation of Exchange is one such model, given by:

\begin{equation}\label{eq:equation_of_exchange}
MV = PQ
\end{equation}

Where:

$ \bullet $  $M$ is the total money supply.

$ \bullet $  $V$ is the velocity of money.

$ \bullet $ $P$ is the price level.

$ \bullet $ $Q$ is the transaction volume (or economic output).